dispRity ecology demo

### 2017-08-15 inst/gitbook/01_glossary.Rmd

-   **Ordinated space**. The mathematical multidimensional object that will be analysed with this package.
    In morphometrics, this is often referred to as the morphospace.
    However it may also be referred to as the cladisto-space for cladistic data or the eco-space for ecological data etc.
    In practice, this term designates an ordinated matrix where the columns represent the dimensions of the space (often – but not necessarily - > 3!) and the rows represent the elements within this space.

-   **Elements**. The rows of the ordinated space. Elements can be taxa, field sites, countries etc.

-   **Dimensions**. The columns of the ordinated space. The dimensions are referred to as axes of variation, or principal components, for ordinated spaces obtained from a PCA.

-   **Subsamples**. Sub-samples of the ordinated space.
    A sub-sample (or subsamples) contains the same number of dimensions as the ordinated space but may contain a smaller subset of elements.
    For example, if our ordinated space is composed of birds and mammals (the elements) and 50 principal components (the dimensions), we can create two subsamples containing just mammals or birds, but with the same 50 dimensions, to compare disparity in the two clades.

>>>>

-   **Multidimensional space**. The mathematical multidimensional object that will be analysed with this package.
    In morphometrics, this is often referred to as the morphospace.
    However it may also be referred to as the cladisto-space for cladistic data or the eco-space for ecological data etc.
    In practice, this term designates a matrix where the columns represent the dimensions of the space (often – but not necessarily - > 3!) and the rows represent the elements within this space.

-   **Elements**. The rows of the multidimensional space matrix. Elements can be taxa, field sites, countries etc.

-   **Dimensions**. The columns of the multidimensional space matrix. The dimensions can be referred to as axes of variation, or principal components, for ordinated spaces obtained from a PCA for example.

-   **Subsamples**. Subsamples of the multidimensional space.
    A subsample (or subsamples) contains the same number of dimensions as the space but may contain a smaller subset of elements.
    For example, if our space is composed of birds and mammals (the elements) and 50 principal components of variation (the dimensions), we can create two subsamples containing just mammals or birds, but with the same 50 dimensions, to compare disparity in the two clades.

### 2017-08-15 inst/gitbook/06_ecology-demo.Rmd

@@

# Data
For this example, we will use the famous `iris` inbuilt data set

@@

# Classic analysis
A classical way to represent this ordinated data would be to use two dimensional plots to look at how the different species are distributed in the petal-space.

@@

# A multidimensional approach with `dispRity`

@@

## Bootstrapping the data
We can the bootstrap the subsamples to be able test the robustness of the measured disparity to outliers.
We can do that using the default options of `boot.matrix` (more about that [here](#bootstraps-and-rarefactions)):

@@

## Calculating disparity

@@

## Summarising the results (plot)
Similarly to the `custom.subsamples` and `boot.matrix` function, `dispRity` displays a `dispRity` object.
But we are definitely more interested in actually look at the calculated values.

@@

## Testing hypothesis

@@

### Setting up a multidimensional null-hypothesis

>>>>

# Ecology demo

@@

## Data
For this example, we will use the famous `iris` inbuilt data set

@@

## Classic analysis
A classical way to represent this ordinated data would be to use two dimensional plots to look at how the different species are distributed in the petal-space.

@@

## A multidimensional approach with `dispRity`

@@

### Bootstrapping the data
We can the bootstrap the subsamples to be able test the robustness of the measured disparity to outliers.
We can do that using the default options of `boot.matrix` (more about that [here](#bootstraps-and-rarefactions)):

@@

### Calculating disparity

@@

### Summarising the results (plot)
Similarly to the `custom.subsamples` and `boot.matrix` function, `dispRity` displays a `dispRity` object.
But we are definitely more interested in actually look at the calculated values.

@@

### Testing hypothesis

@@

#### Setting up a multidimensional null-hypothesis
